### 2021-07-12 src/paper/model/estimated_parameters.tex
Add notation from the parameter tables to the report main text (mostly as comments).

We fit our model to data for Germany from October 2020 until June 2021. We do not use
earlier periods for three reasons. Firstly, in the beginning PCR tests were very scarce
and the reported case numbers unreliable. Secondly, during the summer the case
numbers were extremely low. This could lead to the epidemic going extinct in our
simulation. Thirdly, over the summer, imported cases from touristic travel were likely
important for the infection dynamic but there is not enough data to include them into
our model.

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/infection_channels.png}
    \caption{\textbf{Daily share of infections by contact type}}
    \floatfoot{\noindent \textit{Note:} Daily hare of infections that were contributed
    by each contact type. Darker colors mean that a larger share of infections were
    contributed by that contact type. The majority of infections take place in the
    workplace, in households and via other contacts. Schools and preschools contribute
    less infections, especially after hygiene measures have been introduced.}
    \label{fig:infection_heatmap}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/results/figures/data/other_multiplier}
    \caption{Share of Pre-Pandemic Other Contacts Taking Place with Infection Potential}
    \label{fig:other_multiplier}
    \floatfoot{\noindent \textit{Note:} Values of the other multiplier. All values are
    estimated via the method of simulated moments. The rationale behind each switching
    point is described in Table~\ref{tab:estimated_params}}
\end{figure}

>>>>

We fit our model to data for Germany from mid September 2020 until June 2021. We do not
use earlier periods for three reasons. Firstly, in the beginning PCR tests were very
scarce and the reported case numbers unreliable. Secondly, during the summer the case
numbers were extremely low. This could lead to the epidemic going extinct in our
simulation. Thirdly, over the summer, imported cases from touristic travel were likely
important for the infection dynamic but there is not enough data to include them into our
model.

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/infection_channels.png}
    \caption{Daily share of infections by contact type}
    \floatfoot{\noindent \textit{Note:} Daily hare of infections that were contributed
    by each contact type. Darker colors mean that a larger share of infections were
    contributed by that contact type. The majority of infections take place in the
    workplace, in households and via other contacts. Schools and preschools contribute
    less infections, especially after hygiene measures have been introduced.}
    \label{fig:infection_heatmap}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/results/figures/data/other_multiplier}
    \caption{Share of Pre-Pandemic Other Contacts Taking Place with Infection Potential}
    \label{fig:other_multiplier}
    \floatfoot{\noindent \textit{Note:} Values of the other multiplier. All values are
    estimated via the method of simulated moments. The rationale behind each switching
    point is described in Table~\ref{tab:estimated_params}}
\end{figure}
